### 2017-05-05 conclusions.tex
could ship in theory

\section{Conclusions and Future Work}
\label{conc}

When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}.  By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any very-high-quality fault localizations.

As future work, we plan to apply the mutation-based metric to other
fuzzer taming and fault localization problems.  The highly varying
results for even the best fault localization methods in our
experiments demonstrate that further advances are required before
compiler debugging can consistently be made less onerous through automated
assistance.  One idea is to combine the metric approach and the ideas
in MUSE and MUSEUM, or other mutant-based localizations such as
Metallaxis \cite{Metallaxis} in some way, to exploit passing tests and perhaps
additional coverage information.  We would also be very interested to
compare our localizations with the Metallaxis
\cite{Metallaxis,Papadakis} approach.

>>>>

\section{Conclusions and Future Work}
\label{conc}
\comment{
When are two failing test cases due to the same fault?  This paper
demonstrates that
``when they are repaired by the same program mutants'' is a useful answer to
this question.  The problem of causality in executions is hard, and
has long been tied to a notion of similarity of
executions \cite{NearNeighbor,GroceError}. } By using program changes
(produced by mutants) as
causes to determine distance, it is possible to improve on efforts
to identify the set of faults in a large set of redundant compiler failures
\cite{PLDI13} and discover the source code locations of faults
\cite{MUSE,multilingual}.  For a set of more than 2,800 tests and more
than 50 faults, over the Mozilla SpiderMonkey 1.6 JavaScript compiler and
GCC 4.3.0, our methods improve fault identification (``fuzzer taming''), in a statistically significant way
(with effect size of about 3\% improvement), over
the \emph{best} (for each subject program) of over 16 metrics considered in previous work.
Preliminary investigation also shows improvement (for a shared
mutation testing budget) over previous mutant-based fault localization
methods, for the same tests and a subset of 24 faults with known
locations.  Our {\bf Repair} method, in particular, was the only
localization approach to provide any perfect localizations of faults
(it produced 3),
and provided three times as many very-high-quality (ranking the fault
in top 5 locations) localizations as the next best method
\cite{multilingual}  --- 6 such localizations, compared to only 2.
For GCC wrong-code faults, only our methods produced any very-high-quality fault localizations.

As future work, we plan to apply the mutation-based metric to other
fuzzer taming and fault localization problems.  The highly varying
results for even the best fault localization methods in our
experiments demonstrate that further advances are required before
compiler debugging can consistently be made less onerous through automated
assistance.  \comment{One idea is to combine the metric approach and fall
the ideas
in MUSE and MUSEUM, or other mutant-based localizations such as
Metallaxis \cite{Metallaxis} in some way, to exploit passing tests and perhaps
additional coverage information.  We would also be very interested to
compare our localizations with the Metallaxis
\cite{Metallaxis,Papadakis} approach.}

### 2017-05-05 experiments.tex
could ship in theory

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column shows, for each fault, an ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that repair a failure but also break some passing test, is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  Even with these restrictions, running all mutants on passing tests until at least a single kill was observed took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve is worse compared to the PLDI 2013 curve.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage provides only 16 faults over 31 tests.

@@

Table \ref{bothtable} shows localization results for GCC 4.3.0.  Again, only some faults were deemed to have a strong enough ground truth patches for localization evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 25) localizations.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed very well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD is around 3\%, and statistically significant.

For fault localization and error explanation, the results show possible improvement on state-of-the-art approaches, in the absence of complete information from mutant analysis over passing tests (which can be very expensive to obtain).  A practical impact of the results reported is that we suggest users of our techniques examine only the first few (at most 10, and we propose as few as 5) mutants and coverage-changing statements, and ignore localization if none of these results are helpful.  This is analogous to our suggestion that a user abandon the FPF curve if 5-10 test cases in a row fail to reveal any new faults, as a heuristic.  We suspect the information in the mutants/coverage changes is probably helpful in some cases where they do not localize a faulty line, but this is simply based on our highly incomplete understanding of the faults and patches in question, and not a solidly established claim.  The expertise of compiler developers would be needed to confirm or reject this belief.  Our suggestion that mutations themselves provide interesting error explanation is also applicable to MUSE and MUSEUM.  There may be some potential for confusing explanations, however, if repairs include mutants that also cause some failures, as in the standard MUSE/MUSEUM approach.

 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs. If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate it would usually be faulty.  But such cases are rare:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  We applied our repair localization to the MUSEUM data set, using the full Proteum mutant set and added MUSEUM-specific mutants, and for all but one of the 8 bugs in the data set, our results were equivalent to those for MUSEUM (in one case our approach fails to produce a localization).

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists, and results in {\bf Repair} either providing a ``useful'' localization or no localization at all, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.  For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

@@

Mutation analysis is not cheap.  The experiments in this paper were run over a long period of time.  However, there are numerous ways to reduce costs.  First, the primary cost is compiling the mutated versions of the SUT.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.

Second, and most critically, most program mutants never need to be considered as repairs, because we only consider mutants that cause no passing test case to fail.  MUSE and MUSEUM use kills by passing tests to help rank such tests as repairs, which is finer grained but more expensive.  As we show, MUSE and MUSEUM \emph{can}  be used without passing tests or these mutants, and MUSEUM still produces good results even with a weak oracle and few operators.

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than PLDI 13 best.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were considerably worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  Finally, we have preliminary results indicating that a guided-sampling approach may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.

@@

The largest threat to validity is that this paper's conclusions rely on only two data sets, used in a previous paper.  The fault ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of fault localization.  Generalizing to all compilers, or to software systems that are not compilers, would be unwarranted.  However, for compilers, we believe the underlying arguments supporting the probability of discovering many meaningful repairing mutants should hold in the general case.  There is no particular reason to believe that Csmith and {\tt jsfunfuzz} produce unusual random test cases, and both have often been used to detect faults in compilers other than the two considered in this paper.  For other kinds of software, more experiments are definitely warranted.  It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

Second, the comparison with MUSE and MUSEUM is limited.  MUSE is not really intended for multiple faults.  With our oracles, MUSE and MUSEUM may need the full results from passing tests, and some mutant we omit might be both highly ranked and a good localization.  A full comparison would include a complete analysis of passing tests also, but would likely require far more than 10x the computation time.  Finally, these experiments use Andrews' mutation operators, while MUSE/MUSEUM experiments use Proteum \cite{Proteum}, which has a much larger set of mutation operators, and their results indicate that the large set of operators is important.  However, running all Proteum GCC mutants over all passing tests would likely be prohibitively expensive.

>>>>

Table \ref{bothtable} shows a comparison of three fault localization methods for the SpiderMonkey (and GCC) faults.  The first column is a fault ID. The next three columns show localization rankings.  A dash for a column means that localization did not rank any faulty statements, or assigned all faulty statements suspiciousness of 0.0.  The three rankings are: our {\bf Repair} localization, the MUSE \cite{MUSE} localization, and the MUSEUM \cite{multilingual} localization, which uses the same formula as MUSE, but works better for multiple faults because it uses only one failure.  The MUSE/MUSEUM formulas normally make use of information from passing tests as well: when mutating a statement makes a passing test case fail, it makes the statement \emph{less} suspicious, by a weighted amount. The weight assigned to information from passing tests in our setting would likely be low (due to the ratios of repairs to mutation kills).  In a limited sense, information from passing tests is already incorporated in our results.  Throwing out all mutants that are killed by any passing test as potential repairs/localizations ensures that the rankings of all statements that are in MUSE/MUSEUM rankings are correct, \emph{relative to each other}.  By definition, passing tests have no influence on the suspiciousness of these mutants.  However, there may be other mutants that 1) repair a failure and 2) are killed by some test case: these could, if enough different ones repaired the same faulty statement, improve MUSE/MUSEUM results, though in practice this is extremely unlikely.  We reject such mutants in part to keep costs low, and in part because we think that the causal information contained in such mutants, that ``fix'' a failure but also break some passing test(s), is problematic.  They seem likely to be less useful as explanations of the causes of a failure, since they do not impact the program semantics in a way that is only known to be beneficial, and could potentially even mislead a user if used as explanations.  \comment{Still, it is most useful to compare MUSEUM/MUSE and our approach on the cases where all methods produce a localization.}

Discussion with the MUSE/MUSEUM authors confirms  that adding information for passing tests, while costly, would likely improve the MUSE and MUSEUM results, given the weakness of our oracles, particularly for SpiderMonkey, and should be considered essential for ideal application of their approach.  Because the cost of recording the full mutant analysis matrix for all passing tests (rather than considering a mutant killed as soon as one test fails, as we do) is very high, and we would like to produce a comparison over a fixed computational cost, we give results for MUSE/MUSEUM over failing tests only, cautioning that we are not sure what the impact of this choice is on faults that were not localized.  For similar reasons of keeping costs low, we also used the mutation operators of Andrews vs. the more extensive Proteum \cite{Proteum} operators used in MUSE/MUSEUM's evaluations.  \comment{Even with these restrictions, running all mutants on passing tests until at least a single kill was observed took about 3 times as long as the search for repairs, which we already consider a potentially problematic cost.}  Below we provide some comparisons with MUSEUM and MUSE fault localization in the context of a full mutation result matrix using their preferred set of operators.

@@

There were 377,679 GCC mutants, based on 424,186 lines of code in C and header files. Of these mutants, 73,016 were covered by some failing test case.  Of these mutants, 41,385 survived a GCC bootstrap build, compiled hello world, and passed a GCC test suite.  Of these mutants, 3,232 (7.8\%) repaired at least one test case.  Figure \ref{gcccurves} shows discovery curves for the mutant repair metric vs. the best PLDI 2013 curve, Euclidean distance over function coverage vectors \cite{PLDI13}.  GCC's APFD improvement is larger than that for SpiderMonkey, but its early curve is worse compared to the PLDI 2013 curve.  Using the hypothetical model where a user stops examining tests after a plateau of size 10, the user of the mutant-based taming will see 18 distinct faults by examining 25 tests, and the user of the function coverage based taming will see 20 faults after examining 45 tests.  If a user gives up after a plateau of size 5, our approach again lets a user examine 18 faults over 25 tests.  Function coverage only yields 16 faults over 31 tests.

@@

Table \ref{bothtable} shows localization results for GCC 4.3.0.  Again, only some faults were deemed to have strong enough ground truth patches for evaluation.   MUSE performed poorly, with no useful (by the standard of having at least one faulty statement in the top 25) localizations.  MUSEUM provided 3 useful localizations, but no very high quality localizations.  Only {\bf Repair} performed very well, with useful localizations for 5 faults, and the fault was in the top 5 statements for 4 of these.

@@

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users simply do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique, since trying multiple metrics is impractical, since a user has to examine each curve.  \comment{It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.}  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work; our improvements over any single method applied to both problems are considerably larger.  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD from best-previous method is around 3\%, and statistically significant.

For fault localization and error explanation, the results show possible improvement on state-of-the-art mutation-based approaches.  A practical impact of the results reported is that we suggest users of our techniques examine only the first few (at most 10, and we propose as few as 5) mutants and coverage-changing statements, and ignore localization if none of these results are helpful.  This is analogous to our suggestion that a user abandon the FPF curve if 5-10 test cases in a row fail to reveal any new faults, as a heuristic.  We suspect the information in the mutants/coverage changes is probably helpful in some cases where they do not localize a faulty line, but this is simply based on our highly incomplete understanding of the faults and patches in question, and not a solidly established claim.  The expertise of compiler developers would be needed to confirm or reject this belief.  Our suggestion that mutations themselves provide interesting error explanation is also applicable to MUSE and MUSEUM.  There may be some potential for confusing explanations, however, if repairs include mutants that also cause some failures, as in the standard MUSE/MUSEUM approach.

There are two ways to consider the performance of {\bf Repair}.  First, it is using information that other techniques are not using.  If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate that it would usually be faulty code.  But such cases are very rare in compilers:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  {\bf Repair} can distinguish repairing mutants in fine-grained ways that MUSE and MUSEUM cannot by relying on the onion-ring structure:  when a repair also repairs failures that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults, and so ranks it lower than more ``relevant'' repairs.

The other way to think about {\bf Repair} for the non-compiler faults especially, is as a very \emph{cautious} localization.  It only uses mutants that repair a failure, and, because it is clear that, in general, failing tests contain far more information about faults than passing tests, it only uses information from failures (other than using passing tests to prune mutants that kill some passing tests, again a principle of discarding potentially confusing information).  This results in {\bf Repair} either providing a ``useful'' localization or almost no localization information at all to mislead a user, for the non-compiler faults, which user studies and surveys suggest is the ideal behavior due to the cost of false positives in localization \cite{AutoHelp,Kochhar}.

\comment{
 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  We applied our repair localization to the MUSEUM data set, using the full Proteum mutant set and added MUSEUM-specific mutants, and for all but one of the 8 bugs in the data set, our results were equivalent to those for MUSEUM (in one case our approach fails to produce a localization).}

{ For the compiler faults, if any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

@@

The compiler experiments required a large computational budget.  However, our approach is, by design, cheaper than MUSE or Metallaxis-FL, in that, for a program with up-to-date mutation testing results (just knowing which mutants are killed, not a full matrix), it only requires executing mutants over failing tests.  Running each test case under each mutated version of the compiler is cheap: each execution requires around 0.05 seconds for SpiderMonkey, and 0.12 seconds for GCC, on average; moreover, executions can be done in parallel, most failures do not cover most mutants, and vice versa, so the total number of repair checks needed is far less than the product of mutants and failures, and can be spread over many machines.  \comment{The practical approach to fuzzer taming for a large, ongoing project is likely to maintain a set of ``hot'' pre-compiled mutants.  These can be pruned at will by running them on passing test cases, and removing mutants that fail on any test case.  }

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than PLDI 13 best.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were much worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  \comment{Finally, guided sampling may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.}

@@

The largest threat to validity is that this paper's conclusions rely on only two data sets for compilers.  The fault ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

### 2017-05-05 relatedwork.tex
could ship in theory

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
%The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults. Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

@@

Some approaches to localization or patching assume the possibility of a mutant/change \emph{actually} fixing a fault.  In our experiments, we found this to be highly unlikely -- most of our patches were far larger than the largest higher-order-mutants \cite{jia2009higher} anyone usually considers applying, and none were equivalent to a repair.  Previous work has shown that, across a large body of open source programs in many languages, most fault fixes were larger in size than even low-order higher-order mutants \cite{GopinathMutants}.
We speculate that fixes for compilers may be likely to be even more complex than the average, given that compilers are particularly complex software systems.  
Our primary assumption is simply that similar executions respond similarly to mutants, and in particular executions due to the same fault can be ``repaired'' by similar program changes.  These changes are likely to be \emph{related} in some causal way to the actual fault, but are unlikely to be the actual fault, for reasons of comparative complexity of mutants and real fixes.

>>>>

Fault localization \cite{FaultSurvey,NearNeighbor,Liblit03,Liblit05,Cleve05,Jones2002,Jones05,Jones07,GroceError,ChakiLev,Liu06,SPIN03,Santelices:ICSE:2009,Abreu:2006:PRDC,xuan2014test,DD}, even specifically for compilers \cite{Whalley94}, is a long-standing field of research.  Recently, fault localization researchers have used program mutants to improve statistical \cite{Jones2002} fault localization techniques \cite{MUSE,DebroyMutant,FasterMutant,multilingual,Metallaxis,Papadakis}.
%The core of this work has been the belief that faulty program locations are (1) more likely to change a failing test to successful when mutated and (2) less likely to change a successful test case to faulty when mutated.  This clearly connects to our general notion that how two test cases respond to a set of mutants is a good measure of their semantic similarity.
The work of Hong et al. \cite{multilingual} on MUSEUM and Moon et al. \cite{MUSE} on MUSE provides a good summary of other work along these lines. \comment{, and is perhaps most similar to ours in assumptions, in particular ``Conjecture 1'' that a test case that used to fail on a program is more likely to pass on a mutation of a faulty statement.  While we suggest some localizations as a welcome and interesting side effect of our distance metric and FPF analysis, our primary goal is the discovery of all faults.} Much fault localization work is largely (in many cases exclusively) based on single-fault scenarios; e.g., the MUSE \cite{MUSE} evaluation includes only 2 of 14 scenarios with multiple faults, and those scenarios include only a few faults.   The statistical approaches may owe some of their superiority in experiments over other methods to the use of mostly single-fault evaluations \cite{Jones05}.  By focusing on a single failing test case (for us, selected by fuzzer taming) as the locus of analysis, our work, like some early efforts \cite{NearNeighbor,Cleve05,GroceError} may be more suited for situations involving many faults.  MUSEUM \cite{multilingual} also revisits this approach, combining the MUSE formula with localization using only a single failure.

@@

\comment{
Some approaches to localization or patching assume the possibility of a mutant/change \emph{actually} fixing a fault.  In our experiments, we found this to be highly unlikely -- most of our patches were far larger than the largest higher-order-mutants \cite{jia2009higher} anyone usually considers applying, and none were equivalent to a repair.  Previous work has shown that, across a large body of open source programs in many languages, most fault fixes were larger in size than even low-order higher-order mutants \cite{GopinathMutants}.
We speculate that fixes for compilers may be likely to be even more complex than the average, given that compilers are particularly complex software systems.  
Our primary assumption is simply that similar executions respond similarly to mutants, and in particular executions due to the same fault can be ``repaired'' by similar program changes.  These changes are likely to be \emph{related} in some causal way to the actual fault, but are unlikely to be the actual fault, for reasons of comparative complexity of mutants and real fixes.}
